Baseline centering problem

### 2019-01-11 paper/tangotd.tex

>>>>

Convergence? The true Newton iteration $Z\gets 2Z-Z\Delta Z$ initialized
with $Z=\Id$ converges, and so does the continuous-time version
$Z'=Z-Z\Delta Z$. However, due to sampling of $s_1\sim \rho$, we will (in
the tabular case) have something like $Z'=\rho(Z-Z\Delta Z)$ or (in the
parametric case) $\theta'=\E_\rho (\partial_\theta Z.(Z-Z\Delta Z))$ and
it is not obvious that those converge. (All the problems with TD appear
here as well.) Assuming overparametrization and convergence of supervised
learning for a parametric model $Z_\theta$, one might proceed by
``semi-steps'' as follows: Start with a $\theta_0$, and take the full
Newton step $2Z_{\theta_0}-Z_{\theta_0}\Delta Z_{\theta_0}$ as a
supervised training target for $Z_\theta$; then it does not really matter
what the sampling distribution for this supervised training is, as long
as that sampling distribution covers everywhere.
